Analysis of Shootings and Firearm Discharges in Toronto

### 2024-12-02 paper/paper.qmd
in text citations update

Data cleaning was performed using R[@citeR] packages such as `tidyverse`[@tidyverse] and `lubridate`. The `occ_date` variable was converted to a numeric format to fit the model requirements, and categorical variables were transformed using appropriate factor conversions.

@@

>>>>

Data cleaning was performed using R[@citeR] packages such as `tidyverse`[@tidyverse] and `lubridate`. The `occ_date` variable was converted to a numeric format to fit the model requirements, and categorical variables were transformed using appropriate factor conversions. The cleaning process was rigorously documented to ensure transparency and reproducibility, aligning with best practices outlined by Gebru et al. [@gebru2021datasheets].

@@

This part employed the ggplot2 package [@ggplot2] to create detailed and informative visualizations that effectively illustrate the data trends and insights from our analysis.
